The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-06-28 WavesData-2019/LatexNotes/notes.tex
NM

% New
\newcommand{\depth}{d}
\newcommand{\dup}{\depth^{-}}
\newcommand{\ddn}{\depth^{+}}
\newcommand{\lamup}{\lambda^{-}}
\newcommand{\lamdn}{\lambda^{+}}
\newcommand{\freqp}{f_p}
% New
\newcommand{\meanup}[1]{\mean{#1}_{-}}
\newcommand{\meandn}[1]{\mean{#1}_{+}}
\newcommand{\skw}{\text{skew}}
\newcommand{\var}{\text{var}}

% New
\newcommand{\etastd}{\eta_{\text std}}
\newcommand{\ampp}{\mathcal{A}}
\newcommand{\Gibbs}{\mathcal{G}}
\newcommand{\lamfac}{N}
% New
\newcommand{\Hp}{H^{+}}
\newcommand{\Hm}{H^{-}}
\newcommand{\Gp}{\Gibbs^{+}}
\newcommand{\Gm}{\Gibbs^{-}}

@@

We introduce the following characteristic scales
\begin{align}
&a = \mean{\eta^2}^{1/2} 
&&\mbox{\em upstream characteristic wave amplitude} \\
&\lamup = \sqrt{g \dup} / \freqp
&&\mbox{\em upstream characteristic wave length}
\end{align}
and the dimensionless variables
\begin{align}
&u = \eta/a
&&\mbox{\em dimensionless displacement} \\
&\tilde{x} = \frac{2 \pi \xi}{\lamfac \lamup} = \frac{2 \pi (x-ct)}{\lamfac \lamup}
&&\mbox{\em dimensionless position} \\
& \tilde{t} = 
\end{align}

>>>>

% Basic physical parameters and scales
\newcommand{\depth}{h}
\newcommand{\dup}{\depth^{-}}
\newcommand{\ddn}{\depth^{+}}
\newcommand{\freqp}{f_p}
\newcommand{\lam}{\lambda}
\newcommand{\lamfac}{N}
% More parameters
\newcommand{\etastd}{\eta_{\text std}}
\newcommand{\amp}{a}
% Statistical quantities
\newcommand{\skw}{\text{skew}}
\newcommand{\var}{\text{var}}
% Dimensionless parameters
\newcommand{\epsup}{\eps_0}
\newcommand{\delup}{\delta_0}
\newcommand{\drat}{D}
\newcommand{\ampp}{\mathcal{A}}
% Hamiltonian and Gibbs stuff
\newcommand{\Hp}{H^{+}}
\newcommand{\Hm}{H^{-}}
\newcommand{\Gibbs}{\mathcal{G}}
\newcommand{\Gp}{\Gibbs^{+}}
\newcommand{\Gm}{\Gibbs^{-}}
\newcommand{\meanup}[1]{\mean{#1}_{-}}
\newcommand{\meandn}[1]{\mean{#1}_{+}}

@@

We introduce the following characteristic scales
\begin{align}
&\amp = \mean{\eta^2}^{1/2} 
&&\mbox{\em characteristic wave amplitude} \\
&\lam = \sqrt{g \depth} / \freqp
&&\mbox{\em characteristic wave length}
\end{align}
where $\mean{\cdot}$ indicates the mean of a quantity. Note that the characteristic wavelength $\lam$ takes different values upstream and downstream of the ADC.
We introduce the following dimensionless variables
\begin{align}
&u = \eta/\amp
&&\mbox{\em dimensionless surface displacement} \\
&\tilde{x} = \frac{2 \pi \xi}{\lamfac \lam} = \frac{2 \pi (x-ct)}{\lamfac \lam}
&&\mbox{\em dimensionless position} \\
& \tilde{t} = \freqp^{-1}
\end{align}
Then the dimensionless KdV becomes
\begin{equation}
u_t + \frac{3 \pi}{\lamfac} \epsup \drat^{-1} u u_x + \frac{4 \pi^3}{3 \lamfac^3} \delup^2 \drat u_{xxx} = 0
\end{equation}

Sidenote: If one simply uses the most naive scales, $u = \eta/\amp$, $\tilde{x} = \xi/\lam$, $\tilde{t} = t \freqp$, then the dimensionless KdV is the more standard one:
\begin{equation}
2 u_t + 3 \eps u u_x + \frac{\delta^2}{3} u_{xxx} = 0
\end{equation}
where $\eps = a/h$ and $\delta = h/\lam$.
